Clumpiness and rotation: possible causes for an atypical Lyman-$\alpha$ dwarf galaxy

### 2017-02-23 paper/letter.tex
percentiles

\section{Theoretical Models and Parameter Exploration}

@@

The rotation model corresponds to the work presented in
\citep{GaravitoCamargo2014} based on the Monte Carlo code
\texttt{CLARA} \citep{CLARA}. 
In that model the Ly-$\alpha$ photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the HI line's
center optical  depth $\tau$ measured from the center to its surface, the HI
temperature $T$, and the linear surface velocity $V_{\rm max}$.  
Including the effect of dust only changes the overall line
normalization but not its shape.  
The results we report do not include any dust model.
In this paper we use an analytical solution that captures the most
important effects of rotation onto the \lya\ line as explained by \citet{GaravitoCamargo2014}.

The analytical solution for the rotation sphere is the base to
perform the Markov Chain Monte Carlo (MCMC) calculation using the
\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
is an open source optimized implementation of the affine-invariant 
ensemble sampler for MCMC. 
The algorithm creates a number of walkers that,
during a sufficient number of steps, generate parameters' combinations
for a specific model. For each time, the code calculates the likelihood of the
combination with respect to the observational data. The walkers ecplore
the parameter space sampling the likelihood function.

@@

Figure 1. summarizes our findings.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for a
urotating homogeneous gas sphere (thin line) and the multiphase
model (thick line).

@@

MCMC methods are optimal for sampling parameters at a high number of 
dimensions. In this case we explore flat priors on four parameters:
$200<V_{\rm max}/\mathrm{km\ s}^{-1} <600$,  
$6.0<\log_{10}\tau<9.0$, $4.0<\log_{10} T/10^4\mathrm{K}< 4.5$ and
$0<\theta<90$ using $500$ steps with $24$ walkers for a total of
$12000$ points in the chain. 
The results are summarized in 
Figure \ref{emceeresults}. 
From this model we find that the fiducial 
parameters that could explain the broad features in \tol\ are 
$V_{\rm max}=348^{+75}_{-48}$ km s$^{-1}$, $\log \tau = 6.96^{+0.26}_{-0.18}$, 
$\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$ and $\theta = 35.78^{+2.13}_{-1.88}$ 
degrees.

>>>>

\section{Theoretical Models and Parameter Estimation}

@@

The rotation model corresponds to the work presented in
\citep{GaravitoCamargo2014} based on the Monte Carlo code
\texttt{CLARA} \citep{CLARA}. 
In that model the Ly-$\alpha$ photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the HI line's
center optical  depth $\tau$ measured from the center to its surface, the HI
temperature $T$, and the linear surface velocity $V_{\rm max}$.  
Including the effect of dust only changes the overall line
normalization but not its shape.  
The results we report do not include any dust model.
Here we use an analytical solution that captures the most important
effects of rotation onto the \lya\ line as explained by
\citet{GaravitoCamargo2014} and allows us a full parameter space
exploaration.

The analytical solution for the rotation sphere is the base to
perform a Markov Chain Monte Carlo (MCMC) calculation using the
\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
is an open source optimized implementation of the affine-invariant 
ensemble sampler for MCMC. 
The algorithm creates a number of walkers that,
during a sufficient number of steps, generate parameters' combinations
for a specific model. For each time, the code calculates the likelihood of the
combination with respect to the observational data. The walkers explore
the parameter space sampling the likelihood function built as $\propto
\exp(\chi^2/2)$, where the $\chi^2$ is computed from each bin in the
spectra after normalization.

We explore flat priors on four parameters: $200<V_{\rm
  max}/\mathrm{km\ s}^{-1} <600$,   $6.0<\log_{10}\tau<9.0$,
$4.0<\log_{10} T/10^4\mathrm{K}< 4.5$ and $0<\theta<90$ using $500$
steps with $24$ walkers for a total of $12000$ points in the chain.
We estimate the parameter values from the 16th, 50th and 84th
percentiles.

@@

Figure 1. summarizes our main finding.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for the multiphase model (thick line). 
and the rotating homogeneous gas sphere (thin line).

@@

The results are summarized in 
Figure \ref{emceeresults}. 
From this model we find that the fiducial 
parameters that could explain the broad features in \tol\ are 
$V_{\rm max}=348^{+75}_{-48}$ km s$^{-1}$, $\log \tau = 6.96^{+0.26}_{-0.18}$, 
$\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$ and $\theta = 35.78^{+2.13}_{-1.88}$ 
degrees.
